\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage{geometry}
    \geometry{
        a4paper,
        left=15mm,
        right=20mm,
        top=15mm,
        bottom=15mm
     }
\usepackage{helvet}
\usepackage{multicol}
\renewcommand{\familydefault}{\sfdefault}
\moderncvstyle{casual}
\moderncvcolor{grey}

\firstname{Archit}
\familyname{Mishra}

\title{Resume}

\begin{document}
\begin{center}
 \huge { \textbf{Archit Mishra}}
\end{center}
\begin{center}
 \small {\textit{github.com/armishra}}
 $\cdot$
 \small {\textit{linkedin.com/in/armishra97}}
 $\cdot$
 \small {\textit{archit72@gmail.com}}
 $\cdot$
 \small {\textit{510-449-9633}}
\end{center}

\section{Education}

\cventry{2015 - 2018}{B.S. Computer Science}{}
{UC San Diego}{GPA: 3.78}{
 \begin{itemize}
  \item Expected Graduation: December 2018
  \item Honors/Awards: Tau Beta Pi Engineering Honors Society, Provost Honors
 \end{itemize}
}

\section{Experience}
\cventry{Jun-Sep 2018}{Facebook}{}{Software Engineering Intern - Wormhole Pub/Sub Team}{}{
 \begin{itemize}
  \item Reduced subscriber host failure domain by up to 1000 times by creating
        a thrift server API to narrow failure metrics to single
        subscriptions and act on a subscription level.
  \item Improved subscriber SLA guarantee by implementing stuck subscriber
        thread detection.
  \item Drastically improved oncall tooling for subscriber side issues by
        building a utility for remotely acting on subscriber hosts and tiers.
 \end{itemize}
}

\cventry{Jun-Sep 2017}{Facebook}{}{Software Engineering Intern - Database Engineering Team}{}{
 \begin{itemize}
  \item Automated a previously manual process of recovering auto increment
        values by implementing crash safety into MyRocks server.
  \item Improved deadlocked transaction handling by building transaction
        deadlock detection and tracking in RocksDB and MyRocks.
 \end{itemize}
}

\cventry{Jun-Aug 2016}{Excelfore}{}{Software Development Intern}{}{
 \begin{itemize}
  \item Integrated vehicle IOT services with a low latency video camera stream.
  \item Sped up face detection algorithm by 200\% by implementing a
        prediction algorithm on a 30 MB/s video streaming pipeline.
  \item Improved lane tracking application by minimizing calculations done
        per lane candidate leading to a 70\% speed up.
 \end{itemize}
}

\cventry{2015-Present}{UCSD CSE Department}{}{CS Tutor}{}{
 \begin{itemize}
  \item Undergraduate Tutor for:
        \begin{itemize}
         \item Computer Architecture [CSE 141]
         \item Intro \& Advanced Data Structures [CSE 12, 100]
         \item Software Engineering [CSE 110]
        \end{itemize}
  \item Most recently, assisted students in course on MIPS ISA, CPU
        microarchitecture designs, cache hierarchy, and memory management.
 \end{itemize}
}

\section{Projects}

\cventry{Fall 2017}{Openflow Mininet QOS hack}{C, C++}{}{}{
 \begin{itemize}
  \item Implemented token bucket rate limiting into a simple IP forwarding
        router built on openflow software defined network architecture running on
        Stanford's mininet emulator.
  \item Designed a bandwidth allocation algorithm in order to provide
        differentiated service handling for network packets based on Quality of
        Service.
  \item Constructed config based firewall to filter packets by CIDR addresses.
 \end{itemize}
}

\cventry{Winter 2016}{Java Distributed File System}{Java}{}{}{
 \begin{itemize}
  \item Implemented distributed systems mechanisms such as replication and
        leadership election.
  \item Designed algorithm to chunk files in parallel and send data over TCP
        sockets to slaves intended to replicate file chunks.
  \item Optimized read latency by implementing an in-memory cache for hot
        chunks.
 \end{itemize}
}

\section{Skills/Languages}
% Areas of Interest
\begin{multicols}{2}
 \cventry{}{Skills}{}{}{}{
  \begin{itemize}
   \item Distributed Systems
   \item Databases
   \item Networks
   \item Storage
  \end{itemize}
 }
 \columnbreak
 \cventry{}{Programming Languages}{}{}{}{
  \begin{itemize}
   \item C/C++
   \item Python
   \item Java
   \item SQL
  \end{itemize}
 }
\end{multicols}



\end{document}
