\documentclass[12pt,a4paper,sans]{moderncv}
\usepackage{geometry}
    \geometry{
        a4paper,
        left=15mm,
        right=20mm,
        top=15mm,
        bottom=15mm
     }
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}
\moderncvstyle{casual}
\moderncvcolor{grey}

\firstname{Archit}
\familyname{Mishra}

\title{Resume}

\begin{document}
\begin{center}
  \LARGE { \textbf{Archit Mishra}}
\end{center}
\begin{center}
  \small {\textit{github.com/armishra}}
  $\cdot$
  \small {\textit{linkedin.com/in/armishra97}}
  $\cdot$
  \small {\textit{archit72@gmail.com}}
\end{center}

\section{Education}

\cventry{2015 - 2019}{B.S. Computer Science}{}
{University of California, San Diego}{\textbf{GPA: 3.80}}{
    Expected Graduation: June 2019 \\
    Courses: Computer Networks, Computer Architecture
}

\section{Experience}
\cventry{Jun-Sep 2017}{Facebook}{}{Software Engineering Intern}{C++}{
  \begin{itemize}
    \item Implemented crash safety for MySQL auto increment values by caching
        each table's auto increment values in the MyRocks data dictionary.
    \item Added transactional deadlock tracking infrastructure to RocksDB for
        reporting transacitonal deadlock cycles in MyRocks.
    \item Sped up table statistics queries by 9 times by caching in memory auto
        increment values.
  \end{itemize}
}

\cventry{Jun-Aug 2016}{Excelfore Inc}{}{Software Development Intern}{C++}{
  \begin{itemize}
    \item Integrated vehicle IOT services with a low latency video camera stream in C++.
    \item Sped up face detection algorithm by 200\% by implementing a
      prediction algorithm on a 30 MB/s video streaming pipeline.
    \item Improved lane tracking application by minimizing calculations done
      per lane candidate leading to a 70\% speed up.
  \end{itemize}
}

\cventry{2015-Present}{UCSD CSE Department}{}{CS Tutor}{Java, C, C++}{
  \begin{itemize}
      \item Undergraduate Tutor for Data Structures, Software Engineering, and
          Advanced Data Structures.
      \item Assisted students in implementing Balanced Binary Search Trees, Hashtables,
          Linked Lists, and Tries.
  \end{itemize}
}

\section{Projects}

\cventry{Fall 2017}{Internet Router with Diffserv and Firewall}{C, C++}{}{}{
  \begin{itemize}
      \item Implemented a router that handles IP forwarding, ARP requests and
          replies, firewall functionality, and differentiated packet service.
      \item Designed various packet servicing queues for each interface and allocated
          different relative bandwidth to each packet queue corresponding to the
          packet's Quality of Service.
      \item Implemented simple subtractive router firewall that restricts
          access to a range of servers as a function of packet's Quality of
          Service.
  \end{itemize}
}

\cventry{Winter 2016}{Java Distributed File System}{Java}{}{}{
  \begin{itemize}
      \item Developed a distributed file system in Java that is optimized for
          storing and retrieving many smaller data files.
      \item Designed system to chunk and send files over the network using Java's
          standard library sockets.
      \item Added in memory tables to buffer writes to disk and increase file write
          throughput by 50\%.
  \end{itemize}
}

\section{Skills}
\cventry{Languages \& Skills}{C++, C, Java, Python}{Networks, Computer Architecture, Databases}{}{}{}

\end{document}
